Eco-evolutionary dynamics of finite populations from first principles

### 2023-03-15 ind_files/99_Appendix_A.tex
Remove unneccessary math technicalities

Consider a one-dimensional real It\^{o} process given by $dX_t = \mu(X_t,t)dt + \sigma(X_t,t)dW_t$ on a filtered probability space $\Omega \subseteq \mathbb{R}$ that admits a probability density function $P(x,t)$ on $\Omega \times [0,\infty)$. Let $f:\mathbb{R}\to\mathbb{R}$ be an arbitrary $C^2(\mathbb{R})$ function. By It\^{o}'s formula, we have:

>>>>

Consider a one-dimensional real It\^{o} process given by $dX_t = \mu(X_t,t)dt + \sigma(X_t,t)dW_t$ that takes values in a subset $\Omega \subseteq \mathbb{R}$ and admits a probability density function $P(x,t)$ on $\Omega \times [0,\infty)$. Let $f:\mathbb{R}\to\mathbb{R}$ be an arbitrary $C^2(\mathbb{R})$ function. By It\^{o}'s formula, we have:
